SMT-Boosted Security Types for Low-Level MPC

### 2025-11-14 toplas26/examples.tex
checkpoint

\subsection{Arithmetic Circuits with Beaver Triples}

@@

sshare(x:string, i1:cid, i2:cid) { m[x]@i2 := (s[x] + -r[x])@i1; m[x]@i1 := r[x]@i1 }

@@

precondition: ( BEAVERTRIP("k") ) 
main() {
    sshare("x", 1, 2); sshare("y", 2, 1); sshare("i", 1, 2); sshare("j", 2, 1);
    sum("z","x","y"); mult("k","i","j"); sum("out","z","k");
    open("out")
}
postcondition: ( m["out"]@1 == IDEALF() )
\end{verbatimtab}
\end{fpfig}

\begin{fpfig}[t]{2-party gate library with Beaver Triple multiplication extended with share type annotations.}{fig-beaver-types}
\footnotesize
\begin{verbatimtab}
sshare(x:string, i1:cid, i2:cid) {
   m[x++"s"]@i1 := (s[x] + -r[x])@i2; m[x++"s"]@i2 := r[x]@i2;
   [m[x++"s"]@i1,m[x++"s"]@i2] : shares
}

@@

precondition: ([m[x]@i1, m[x]@i2] : shares,
	       [m[a]@i1, m[a]@i2] : shares)
secopen(d:string;x:string,a:string) {
    sum(d, x, a); open(d);
    m[d++"p"]@1 as RECON(x) + r[x++a]@o;
    <m[d++"p"]@1> : public;
    <m[d++"p"]@2> : public
}

@@

@@

\subsection{Confidentiality Examples}

%\input{gmw}

In the 2-party GMW protocol \cite{evans2018pragmatic}, another garbled
binary circuit protocol, values are encrypted in a manner similar to
BDOZ as described in Section \ref{section-ipj}. In our definition of
GMW we use the convention that shared values $\macgv{\mesg{w}}$ are
identified by strings $w$ and encoded as shares $\mx{w}{1}$ and
$\mx{w}{2}$.  As for YGC, ciphertypes reflect the confidentiality of
GMW input encodings as defined in the $\ttt{encodegmw}$ function in
Figure \ref{fig-gmw}. No programmer annotation is needed given the
syntax of the function body. More interestingly, the $\ttt{andgmw}$
gate definition shows how a programmer hint can express the relevant
confidentiality property of the output share $\mx{z}{2}$ on client 2,
using the $\ttt{as}$ casting. The non-trivial equivalence can be
verified by SMT once during verification, and subsequently
confidentiality is expressed in the dependent type of the function (as
for $\ttt{encode}$).

Note also that the $\ttt{andgmw}$ function is decorated with a
postcondition that expresses the correctness property of the
function. Although not strictly necessary for confidentiality, this
annotation can at least help eliminate bugs, and also can be used
compositionally for whole-program correctness properties. As for
confidentiality hints, this postcondition needs to be verified only
once at the point of definition and subsequently is guaranteed to hold
for any application.

\subsection{Integrity Examples}

% \input{bdoz}

Returning to the example of malicious-secure 2-party BDOZ arithmetic
circuits begun in Section \ref{section-ipj}, in Figure \ref{fig-bdozsum} we
define $\ttt{sum}$ and $\ttt{open}$ functions. The latter implements
``secure opening''-- each party sends it's local share of a
global value $\macgv{\mesg{w}}$ along with its MAC to the other party,
which is authenticated via the $\macbdoz{w}$ check (in \ttt{\_open}),
and then each party reconstructs $\macgv{\mesg{w}}$. The preconditions
of $\ttt{open}$ specify the authentication requirements.

The $\ttt{sum}$ function implements an addition gate. This is
non-interactive-- each party just sums its local shares
of the two values. The pre- and postcondition annotations
on $\ttt{sum}$ express the additive homomorphism associated
with this encryption scheme-- the sum of MACs of the input
shares is a valid MAC for the output share on each client,
which can be checked using the sum of keys of the input shares.

@@

A common approach to implementing multiplication gates in a BDOZ
setting is to use \emph{Beaver Triples}. Recall that Beaver triples
are values $a,b,c$ with $a$ and $b$ chosen randomly and $c = a * b$,
unique per multiplication gate, that are secret shared with clients
during pre-processing.  In our encoding we assume the additional
convention that each gate output identifier distinguishes the Beaver
triple, so for example the share of the $a$ value for a gate
$\ttt{"g1"}$ is identified by $\ttt{"g1as"}$, etc.

%, and $\eqspre$
%subsumes the following constraints for the $a,b,c$ values of gate
%$\ttt{"g1"}$.  {\footnotesize$$
%\begin{array}{l}
%\mx{\ttt{"g1as"}}{1} \eop \rx{\ttt{"g1as"}}{1}\ \wedge 
%\mx{\ttt{"g1bs"}}{1} \eop \rx{\ttt{"g1bs"}}{1}\ \wedge\\
%\mx{\ttt{"g1as"}}{2} \eop \rx{\ttt{"g1as"}}{2}\ \wedge 
%\mx{\ttt{"g1bs"}}{2} \eop \rx{\ttt{"g1bs"}}{2}\ \wedge\\
%\mx{\ttt{"g1cs"}}{1} \eop \\
%\qquad ((\mx{\ttt{"g1as"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})\ \ftimes\\
%\qquad\phantom{(}(\mx{\ttt{"g1bs"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})) \fminus \rx{\ttt{"g1cs"}}{2}\ \wedge\\
%\mx{\ttt{"g1cs"}}{2} \eop \rx{\ttt{"g1cs"}}{2}
%\end{array}
%$$}

>>>>

@@

genshares(x:string, i1:cid, i2:cid) { m[x]@i2 := (s[x] + -r[x])@i1; m[x]@i1 := r[x]@i1 }

@@

precondition: ( BEAVERTRIP("k") ) 
main() {
    genshares("x", 1, 2); genshares("y", 2, 1); genshares("i", 1, 2); genshares("j", 2, 1);
    sum("z","x","y"); mult("k","i","j"); sum("out","z","k");
    open("out");
    out@1 = m["out"]@1; out@2 =  m["out"]@2

}
postcondition: ( out@1 == IDEALF() AND out@2 == IDEALF() )
\end{verbatimtab}
\end{fpfig}

\subsection{Arithmetic Circuits with Beaver Triples}
\label{section-beaver}

In Figure \ref{fig-beaver} we define a 2-party arithmetic circuit with
4 input gates, 3 internal gates, and 1 output gate. The ideal functionality
is defined as $\ttt{IDEALF}$. As in GMW or BDOZ, circuit wire values
are represented as additive secret shares between two clients we call
$\ttt{1}$ and $\ttt{2}$. As in the GMW example discussed in Section
\ref{section-metaty}, we use string idenfiers $g$ to distinguish
gates, and gate output wire shares are defined as identifiers
$\mx{g}{1}$ and $\mx{g}{2}$. The function $\ttt{RECON}$
represents share reconstruction \emph{in constraints} (not the
protocols themselves). Input gates are
implemented using the $\ttt{genshares}$ function as described in
Section \ref{section-sty}. The $\ttt{open}$ function
implements a federation reveal of a shared value through
share broadcast and reconstruction.

A \ttt{sum} gate can be defined non-interactively using the
homomorphic addition. The correctness \ttt{postcondition} is simple
and perhaps unecessary to accelerate circuit verification, but is
appealing declaratively.  The multiplication gate \ttt{mult} is more
complex. We use the common approach of \emph{Beaver Triples}
\cite{evans2018pragmatic}. Recall that Beaver triples are values
$a,b,c$ with $a$ and $b$ chosen randomly and $c = a * b$, unique per
multiplication gate, that are secret-shared with clients during a
pre-processing phase by an assumed oracular client $\ttt{3}$.
The uniqueness requirement is necessary because
$a$ and $b$ are random values that serve as OTP masks for secure
openings, implemented as \ttt{secopen}. In our encoding we follow the
convention that each gate output identifier distinguishes the Beaver
triple, so for example the share of the $a$ value for a gate
$\ttt{"g"}$ is identified by $\ttt{"ga"}$, etc. The correctness
property of the multiplication gate, expressed as a
\ttt{postcondition}, relies on the $\ttt{BEAVERTRIP}$
precondition. This compositional correctness property can then be used
in circuit construction, without the need for ``re-proof'' in our
Hoare logic inference.

The circuit itself is constructed in \ttt{main} using these
gates. This is a small example but arbitrarily large circuits
can be constructed with this library. The precondition of
\ttt{main} must require distinct Beaver triples for each
multiplication gate in the circuit. The postcondition allows
verification of circuit correctness-- that the protocol
output is equal to the ideal functionality $\ttt{IDEALF}$.

\subsection{Share Type Annotations.}

\begin{fpfig}[t]{2-party gate library with Beaver Triple multiplication extended with share type annotations.}{fig-beaver-types}
\footnotesize
\begin{verbatimtab}
genshares(x:string, i1:cid, i2:cid) {
   m[x++"s"]@i1 := (s[x] + -r[x])@i2; m[x++"s"]@i2 := r[x]@i2;
   [m[x++"s"]@i1,m[x++"s"]@i2] : shares
}

@@

precondition: ([m[x]@i1, m[x]@i2] : shares,
	       [m[a]@i1, m[a]@i2] : shares)
secopen(d:string;x:string,a:string) {
    sum(d, x, a); open(d);
    m[d++"p"]@1 as RECON(x) + r[x++a]@3;
    <m[d++"p"]@1> : public;
    <m[d++"p"]@2> : public
}

@@

In Figure \ref{fig-beaver-types} we extend our previous gate definitions with
share type annotations to enforce confidentiality. The core idea is that
wire values must be \ttt{share}s. The \ttt{genshares}
function includes an annotation specifying that all input gates establish
the $\ttt{shares}$ invariant for wire values. In the \ttt{sum} function,
the \ttt{share} type preconditions for input wires are specified. The
output wire shares can be declared as \ttt{share}s without any coercion
needed, since given preconditions our typing algorithm ($\Vdash$) is
able to check the use of homomorphic addition.

We add coercions and typing assertions to the $\ttt{secopen}$ function
to specify properties of secure openings. After noninteractively
summing a wire value $\ttt{x}$ and a random Beaver triple value
$\ttt{x++a}$, the federation can publicly open the value since it is
masked by the random value. This is expressed using the coercion
$\ttt{as RECON(x) +  r[x++a]@3}$.

\subsubsection{Malicious-Secure Arithmetic Circuits}

@@

@@

### 2025-11-14 toplas26/sty.tex
checkpoint

Both interactive and non-interactive judgements leverage the use
of SMT interpretations as described in Section \ref{section-smt}.
We introduce a \emph{share type} language $\sty$, classifying
\emph{share terms}. We represent share terms using standard notation
\cite{10.1007/978-3-030-68869-1_3}. A share term $[\phi_1,\phi_2]$
represents a secret-shared value where client 1 has $\phi_1$ and
client 2 has $\phi_2$, and this shared value can be reconstructed
as $\phi_1 + \phi_2$.\cnote{Comment on generation and
  reconstruction in general somewhere.} A share term $\pubx{\phi}$
denotes a publicly shared value.
$$
\begin{array}{rcl@{\hspace{10mm}}l}
  \sty &::=& \sharety \mid \pubty \mid \outty & \textit{share types} \\
  \stt &::=& [\phi,\phi] \mid \pubx{\phi} & \textit{share terms} 
\end{array}
$$
Intuitively, the meaning of share types $\sty$ are as follows.
When we ascribe the type $[\phi_1,\phi_2] : \sharety$, this
means that $[\phi_1,\phi_2]$ are shares of their
reconstruction, which we can represent as $\phi_1 + \phi_2$
as discussed in Section \ref{???}. 
In particular, each of $\phi_1$ and $\phi_2$ independently
reveal nothing about $\phi_1 + \phi_2$. Likewise,
$\pubx{\phi} : \outty$ means that $\phi$ has been
publicly \emph{revealed} via broadcast shares, and our
type system requires that $\phi \eop \phi_1 + \phi_2$ with
$[\phi_1,\phi_2] : \sharety$. This implies that the
process of revealing $\phi$ reveals nothing besides $\phi$.
The ascription $\pubx{\phi} : \pubty$ is similar, with the
additional meaning that $\phi$ is a publicly-known value
independent of any client inputs. This includes known
constant values used in protocols, and more interestingly
\emph{secure openings}. Secure openings are commonly used
to interactively compute public values that are masked with
OTPs secret-shared with clients in initialization protocols,
as for example in Beaver Triple multiplication which
we discuss in Section \ref{section-examples}.

@@

>>>>

Both interactive and non-interactive judgements leverage the use
of SMT interpretations as described in Section \ref{section-smt}.
We introduce a \emph{share type} language $\sty$, classifying
\emph{share terms}. We represent share terms using standard notation
\cite{10.1007/978-3-030-68869-1_3}. A share term $[\phi_1,\phi_2]$
represents a secret-shared value where client 1 has $\phi_1$ and
client 2 has $\phi_2$, and this shared value can be reconstructed
as $\phi_1 + \phi_2$.\cnote{Comment on generation and
  reconstruction in general somewhere before this section?.} A
share term $\pubx{\phi}$ denotes a publicly shared value.
$$
\begin{array}{rcl@{\hspace{10mm}}l}
  \sty &::=& \sharety \mid \pubty \mid \outty & \textit{share types} \\
  \stt &::=& [\phi,\phi] \mid \pubx{\phi} & \textit{share terms} 
\end{array}
$$
Intuitively, the meaning of share types $\sty$ are as follows.
When we ascribe the type $[\phi_1,\phi_2] : \sharety$, this
means that $[\phi_1,\phi_2]$ are shares of their
reconstruction, which we can represent as $\phi_1 + \phi_2$
as discussed in Section \ref{???}. 
In particular, each of $\phi_1$ and $\phi_2$ independently
reveal nothing about $\phi_1 + \phi_2$. Likewise,
$\pubx{\phi} : \outty$ means that $\phi$ has been
publicly \emph{revealed} via broadcast shares, and our
type system requires that $\phi \eop \phi_1 + \phi_2$ with
$[\phi_1,\phi_2] : \sharety$. This implies that the
process of revealing $\phi$ reveals nothing besides $\phi$.
The ascription $\pubx{\phi} : \pubty$ is similar, with the
additional meaning that $\phi$ is a publicly-known value
independent of any client inputs. This includes known
constant values used in protocols, and more interestingly
\emph{secure openings}. Secure openings are commonly used
to interactively compute public values that are masked with
OTPs secret-shared with clients in initialization protocols,
as for example in Beaver Triple multiplication which
we discuss in Section \ref{section-examples}.

@@

\begin{theorem}
  If $\prog,\Gamma,R : {OK}$ and $\Gamma$ is closed
  for $\prog$, then $\prog$ satisfies noninterference modulo output. 
\end{theorem}
